---
title: "individual2"
author: "Michael Egle; GitHub: michaelegle"
date: "2/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)

choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")

head(choco)
```

```{r}
choco %>%
  ggplot(aes(x = Rating)) +
  geom_histogram(binwidth = .25)
```

A majority of the chocolate ratings are concentrated around 3 to 3.5. There are a few outliers on the histogram. One chocolate received a perfect rating of 5 and it appears a few chocolates received a rating of 1.
 
```{r}
choco %>%
  ggplot(aes(x = Cocoa.Pct, y = Rating)) +
  geom_point()
```
 
It appears that there's not much correlation between the cocoa percentage in the chocolate and the rating that the chocolate received. Let's use the cor() function to confirm

```{r}
cor(x = choco$Cocoa.Pct, y = choco$Rating)
```

This confirms our original belief. There is very little to no correlation between the cocoa percentage and the rating.
