---
title: "Lab 2"
author: "Michael Egle and John Chandara; GitHub: michaelegle and mrpotatofactory"
date: "2/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)

choco <- read.csv("https://xdaiisu.github.io/ds202materials/hwlabs/choco.csv")
```



# 1. What is the overall number of chocolate bars rated?


Amount of duplicated rows.

```{r}
nrow(choco[! duplicated(choco), ]) - nrow(choco)
```

```{r}
length(choco$Rating)
```

Because there are no duplicates, we can conclude there are 1852 rated bars.


# 2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports.
```{r}
choco %>%
  group_by(Review.Date) %>%
  summarize(numRatings = n()) -> choco_ratings

choco_ratings %>%
  ggplot(aes(x = Review.Date, y = numRatings)) +
  geom_bar(stat = "identity")
```

The number of ratings gradually increases with a peak in 2015 and then a decrease in 2016 and 2017.



# 3. Which are the three locations with the most ratings? How do ratings compare across these company locations?

```{r}
AggRatings <- choco %>%
  group_by(Company.Location) %>%
    summarize(AggRatings.Location = n()) %>%
      arrange(desc(AggRatings.Location)) 

MostPopular <- head(AggRatings, 3)

print(MostPopular)

choco %>%
  filter(Company.Location == 'U.S.A.') %>%
    pull(Rating) %>%
      summary()
```

# 4. Brainstorm and write down an interesting question that can be answer from the dataset. The question should not duplicate the questions above.

Which bean origin yields the highest average rating?

# 5. Answer the question from the dataset.

```{r}
choco %>%
  group_by(Specific.Bean.Origin) %>%
  summarize(avg = mean(Rating), count = n()) %>%
  arrange(desc(avg)) -> choco.origin

choco.origin
```

There's a lot of bean origins that have only produced one chocolate in the database. Let's filter that to only origins that have produced 10 or more chocolates in the database.

```{r}
choco.origin %>%
  filter(count >= 10) -> choco.origin.10

choco.origin.10
```

It appears that Porcelana has yielded the highest average rating of all the bean origins that have 10 or more chocolates in the database with an average rating of 3.36.

# 6. Write one paragraph commenting on the workflow.

Johnny and I split the work up pretty evenly and I think we worked pretty well together as a team. We both have different skill sets to offer on this lab. He's more experienced in overall programming and knows more about Git. Whereas I'm more experienced in R, so we were able to work together and help each other out when we had questions. 
